Optimal Pricing and Informal Sharing: \\ Evidence from Piped Water in Manila

### 2018-09-20 phil_paper/jmp_wjv_v2.tex
lots of fixes to jmp paper

This section details how households choose their monthly quantities of consumption holding their water source fixed.  For households using piped water, this consumption choice is complicated by four features:  (1) households may have difficulty targeting their exact monthly consumption levels; (2) increasing marginal prices in the water tariff result in non-linear budget constraints; (3) households that share a connection need to determine how to divide the monthly water bill; and (4) households fetching from a neighbor may face additional hassle costs in transporting water.  Since the data record monthly consumption for each connection, this model first introduces individual household demand before aggregating household demand at the connection-level for estimation.

Households that use piped water face the difficult task of coordinating water consumption among all household members.  For example, consider a household head trying to manage water consumption across all of their household members each month.  This task would involve monitoring the meter located outside of their dwelling and observing water use among all members.\footnote{Given that many developing countries feature steeply increasing prices with monthly usage, these coordination challenges may magnify any distortions caused by non-linear pricing.}  Mobile survey data indicate that \input{tables/no_info}\unskip\% of surveyed household members do not recall how much they paid for water in the last month while \input{tables/no_use}\unskip\% do not recall the amount that their household consumed in the previous month.

As a simple way to capture this coordination task, the model assumes that each household $i$ sets a goal for water use each month, $w_i$, knowing that idiosyncratic factors, $\epsilon_i$, may increase or decrease the realized amount of usage.  Consumption shocks, $\epsilon_i$, are assumed to be unobserved to the household and independent across time, bringing the total realized water consumption each month to, $W_i=w_i+\epsilon_i$.  Household utility over water, $W_i$ and a numeraire good, $x_i$ is assumed to take the following shape:
\begin{align}\label{equation:umaxfirst}
\begin{split}
U(x_i,W_i) &=  x_i + W_i - \frac{1}{2\alpha_i } ( W_i - \Gamma_i + \alpha_i )^2  \\
W_i &= w_i + \epsilon_i \\
\epsilon_i &\sim \mathcal{N}(0,\Sigma_{\epsilon})
\end{split}
\end{align}
Following from quasi-linear preferences, this quadratic form for utility eliminates income effects and includes a natural satiation point for water consumption, capturing the tendency of households to target specific consumption levels despite low or zero marginal prices as in Figure~\ref{figure:consumptionhistogram}.  Household preferences for water are characterized by $\Gamma_i$, which can be interpreted as a fixed preference for water each month and $\alpha_i$, which captures the extent to which households are price sensitive.  These terms have clearer interpretations in the demand function below.  The exogenous shock to consumption, $\epsilon_i$, is assumed to be drawn from a multivariate normal distribution, $\Sigma_{\epsilon}$ with zero mean, variance terms, $\sigma_{\epsilon}^2$, and allowing for correlation with neighboring households, ${\rho}^{\epsilon}_{i,j}$.  Although households cannot anticipate the exact realization of $\epsilon_i$, they are assumed to understand the distribution of possible shocks, allowing them to maximize expected utility.
\subsubsection{Determining the Budget Constraint}
The household problem is additionally complicated by the presence of non-linear price schedules for water.  Figure~\ref{figure:tariff} provides the increasing tariff in Manila.  The non-linear price schedule produces kinks in household budget constraints leading to non-linear demand functions.  Let $P(W_C) = \{ p^{1},...,p^{K},\overline{W}^{0},...,\overline{W}^{K}\}$ describe tariff schedule as a function of total consumption for the water connection, $W_C = \sum_{i=1}^{S} W_i$.  The tariff includes $K$ segments where segment $k$ corresponds to price $p^{k}$ for water consumption between the consumption thresholds (or kink points), $\overline{W}^{k-1}$ and $\overline{W}^{k}$:
\begin{align*}
P(W_C)=&  
\begin{cases}
      p^{1} &\text{ if } W_C \in [\overline{W}^{0}(=0),\overline{W}^{1}], \\
      p^{2} &\text{ if } W_C \in [\overline{W}^{1},\overline{W}^{2}], \\
      ...   &\text{ ...}, \\
      p^{K} &\text{ if } W_C \in[\overline{W}^{K-1},\overline{W}^{K}(=\infty)]
    \end{cases}
\end{align*}
Given prices and household utility, the final ingredient for characterizing consumption choices is the budget constraint.  The budget constraint includes monthly household income, $Y_i$, and monthly fixed costs of using the water connection, $F_i$, which are assumed to capture three components: (1) monthly service fees, (2) initial connection fees amortized in monthly terms for the duration of the connection, and (3) unobserved, fixed hassle costs associated with setting up a connection, which are also amortized into monthly terms.  Data does not track household water source choices over time in a comprehensive way, which limits the extent to which the model can distinguish between one-time connection costs and monthly service/maintenance costs.  This limitation means that the model cannot address the optimal timing of fixed payments or capture any potential heterogeneity in monthly fixed costs.

Water sharing relationships impact monthly consumption choices through the budget constraint in three ways.\footnote{While the formation of these relationships is discussed in more detail in Section~\ref{section:watersourcechoice}, this section takes these sharing relationships as exogenously given.}  To develop notation for sharing, normalize $i=1$ to be the owner of the connection and define the total number of sharing households for a particular connection as $S$.

First, this model assumes that the monthly water bill is split evenly between all sharing households.  Descriptive evidence suggests that challenges observing and coordinating usage within members of a household also extend across households.  Among owners of the water connection responding to the mobile survey, \input{tables/bill_split}\unskip\% report splitting the water bill evenly or alternating payment each month, \input{tables/bill_fixed}\unskip\% charge sharing households a fixed amount each month regardless of their consumption, and \input{tables/bill_usage}\unskip\% charge other users a price according to their usage.\footnote{The remaining households report ``I don't know'' or ``other.''}  Evenly splitting the bill, alternating payment, or charging a fixed amount provide easy ways to extract compensation without requiring specific information on the monthly consumption of each sharing household.  Yet, these methods also introduce free-rider incentives since households do not have to fully pay for their contributions to the total water bill.  Since data limitations prevent identifying the specific type of contract associated with each shared connection, the model assumes that all households evenly split the bill and explores the theoretical and empirical implications of alternate models in Appendix~\ref{appendix:fixedprice}.  The model captures bill splitting by dividing the total monthly payment for a water connection across the $S$ sharing households.

%\footnote{Under the additional assumption that households never directly observe the $\epsilon$ shocks, splitting the bill provides an intuitive way to ensure all households account for at least some of their usage.  }
Second, sharing households may face a hassle cost, $p_h$, per unit of water, which captures any inconvenience associated with using water from a neighbor's tap.  The mobile survey reveals that among households accessing water from a neighbor's connection, \input{tables/access_fetch}\unskip\% fetch water with containers, \input{tables/access_single_tap}\unskip\% access water from a single hose/pipe provided by the connection owner, and \input{tables/access_pipes}\unskip\% are able to fully connect their household plumbing near the water meter.  These different modes of access suggest that sharing households may face higher time costs fetching water or lower water pressure from piping water additional distances.  Without data on the sharing mode and distance between households for each connection, the model assumes all sharing households, normalized as $i>1$, face a homogeneous hassle cost, $p_h$, from using a neighbor's connection.\footnote{Section~\ref{section:hasslecostestimation} discusses the extent to which this assumption may bias estimates.}  The partitioning of the city into sharing neighborhoods also imposes the implicit assumption that hassle costs rise substantially between neighborhoods so that no household has an incentive to share with households in another neighborhood.  Hassle costs for household $i$ are given by the following function:
\begin{align*}
H_{i} =& 
\begin{cases}
0     &  \text{ if } i=1 \text{ (connection owner) }\\
p_h   &  \text{ if } i \neq 1
\end{cases}
\end{align*}
Third, sharing households must negotiate over how to pay the monthly fixed fees.  The model assumes that households commit to dividing any fixed fees at the start of the sharing arrangement.  Under quasi-linear utility, any fixed transfers are exogenous to monthly consumption decisions.  For ease of exposition, this section assigns a fixed fee, $F_i$ to each household and postpones discussion of how the total fixed fee may be divided between households to Section~\ref{section:watersourcechoice}.

Normalizing the price of the numeraire good, $x$, to one, the budget constraint for household, $i$, using a connection with households, $S$, takes the following form:
\begin{align*}
Y_i - F_i &=  
\begin{cases}
      x_i + H_{i} W_i + \frac{1}{S} p^{1} W_C   &\text{ if }   W_C \in [0,\overline{W}^{1}], \\
      x_i +  H_{i} W_i +  \frac{1}{S} \big [p^{k} W_C -  E_{k} \big]     &\text{ if } W_C \in [\overline{W}^{k-1},\overline{W}^{k}], \\
      ...   &\text{ ... }      
\end{cases} \\
E_{k} &= \big  [\sum_{j=1}^{k-1}  (p^{k} - p^{j})(\overline{W}^{j}-\overline{W}^{j-1})  \big ]
\end{align*}

$E_{k}$ represents the discount that the household earns on all previous price thresholds below the current level of consumption.  This term is calculated by subtracting the current price that the household faces, $p^{k}$, from the previous prices and multiplying by their exposure given by, $(\overline{W}^{j}-\overline{W}^{j-1})$.  In the case where a household uses a connection individually, this expression simplifies by setting the index, $i$, and the total using households, $S$, both equal to one.  In this scenario, the household does not face any hassle costs, $p_h$, and pays the total bill from its corresponding consumption.

@@

When households share a water connection, the consumption choice for each household becomes a strategic decision.  Since prices are non-linear, the total consumption level for each connection, $W_C$, determines the marginal price faced by all households.  For example, with an increasing block tariff like Figure~\ref{figure:tariff}, one household's choice to increase consumption may produce a higher marginal price for other sharing households.   Rewriting the utility function in equation (\ref{equation:umaxfirst}) by substituting the numeraire good, $x$, with the budget constraint, expected utility for household $i$ over the consumption shocks takes the following form:
%\begin{comment}
\scalebox{.88}{\parbox{1\linewidth}{
\begin{align*}
E[U(x_i,w_i)] = &  (Y_i - F_i)  - \frac{1}{S} \sum_{k=1}^{K} \int_{\overline{W}^{k-1}-W_C}^{\overline{W}^{k}-W_C}\big [p^{k} W_C -  E_{k} \big] d \epsilon_C + \int_{-\infty}^{\infty} W_i - H_{i} W_i - \frac{1}{2\alpha_i} ( W_i - \Gamma_i + \alpha_i )^2 d \epsilon_i  \\  
          = &  (Y_i - F_i)  - \frac{1}{S} \sum_{k=1}^{K} \int_{\overline{W}^{k-1}-W_C}^{\overline{W}^{k}-W_C}\big [p^{k} W_C d -  E_{k} \big] d \epsilon_C+ w_i - H_{i} w_i - \frac{1}{2\alpha_i} ( w_i - \Gamma_i + \alpha_i )^2 + \sigma_{\epsilon}^{2}  
\end{align*}
}} \\
Where $\epsilon_C$ is the convolution of consumption shocks across sharing households distributed as follows:
\begin{align*}
          \epsilon_C &\sim \mathcal{N}(0,\sigma_{\epsilon_C}^2 = \sum_{i=1}^{S} \sigma_{\epsilon}^2 + \sum_{i=1}^{S} \sum_{j>i}^{S} \sigma_{\epsilon}^2 \rho^{\epsilon}_{i,j} )
\end{align*}
To solve this system, the model assumes that households follow a perfect information, pure-strategy Nash-Equilibrium in choosing consumption.  Using this structure, households compute their best response consumption functions to arrive at a symmetric equilibrium taking consumption for their sharing partners as given.  
% % % % % % % % % % % % % % % % \footnote{  APPENDIX PROVES THIS;  NEED TO GO DEEPER PLEASE!!! SHOW EXPLICITLY }  % % % % % % % % % % % % % % % % % % %
%Because of the quadratic shape of the utility function, the exogenous shock to consumption, $\epsilon_s$, only affects the optimal consumption choice to the extent that it pushes the household across price thresholds.  Therefore, the solution to equation (\ref{equation:umaxfirst}) is isomorphic to removing the $\epsilon_s$ terms from the utility function and only allowing these shocks to enter through the budget constraint.  This simplification ensures that the $\epsilon_s$ terms enter linearly into the optimization problem through the budget constraint.

@@

The best-response functions for each household can be solved and summed across all sharing households $S$ to form demand at the level of each connection, $C$.  The optimal demand function takes a piecewise form depending on the proximity of different price segments.\footnote{This approach is only relevant for strictly increasing block tariffs since in this case, the budget constraint is convex.  Tariffs that include both increasing and decreasing block tariffs require comparing indirect utilities across all segments.  I take this calculation into account when allowing for decreasing marginal prices in the counterfactual exercises.}  The aggregate demand function is as follows (where $L,M,H$ index low, medium, and high prices relative to each segment):\footnote{For ease of exposition, I use notation where $D^{l}_C=D^{l,l,l}_C$ and $D^{l,j}_C=D^{l,j,j}_C$.}
\begin{align}\label{equation:generaldemand}
\begin{split}
w^{*}_C &=
\begin{cases}
D^{1}_C   & \text{ if } \hspace{1.7cm}                                               \frac{ \eta_C }{ V_{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
D^{1,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
D^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
D^{2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
D^{3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
D^{3,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
D^{4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
\end{cases}\\
\text{Where: } & \\
D^{L,M,H}_C        		&=  d^{L,M,H}_C + \frac{ \eta_C }{ V_{H,L} }   \\
d^{L,M,H}_C       		&= \frac{ 1}{ V^{L,H} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{H} + p^{L} - \overline{W}^{H} (\frac{p^{H} - p^{M}}{\sqrt{2}{\sigma_{\epsilon_C}}})  - \overline{W}^{M} (\frac{p^{M} - p^{L}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ]  \Big )    \\
V^{L,H} 	     	    &=   1 + \frac{\alpha_C}{2 S} ( \frac{p^{H} - p^{L}}{\sqrt{2}\sigma_{\epsilon_C}})   \\
\overline{\eta}^{j}_{l,L}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) - \sqrt{2} \sigma_{\epsilon_C} \\
\overline{\eta}^{j}_{l,U}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) + \sqrt{2} \sigma_{\epsilon_C} \\
\end{split}
\end{align}

>>>>

%This section details how households choose their monthly quantities of consumption holding their water source fixed.

%For households using piped water, they have to consider four aspects when choosing how much to use each month:  (1) households may have difficulty targeting their exact monthly consumption levels since meters can be hard to observe and many family members use the same tap; (2) increasing marginal prices in the water tariff mean that households face non-linear budget constraints; (3) households that share a connection need to determine how to divide the monthly water bill; and (4) households fetching from a neighbor may face additional hassle costs in transporting water.

%Since the data record monthly consumption for each connection, this model first introduces individual household demand before aggregating household demand at the connection-level for estimation.

In choosing how much water to use each month, households using piped water face the difficult task of coordinating water consumption among all household members.  For example, consider a household head trying to manage water consumption across all of their household members each month.  This task would involve monitoring the meter located outside of their dwelling and observing water use among all members.\footnote{Given that many developing countries feature steeply increasing prices with monthly usage, these coordination challenges may magnify any distortions caused by non-linear pricing.}  Mobile survey data indicate that \input{tables/no_info}\unskip\% of surveyed household members do not recall how much they paid for water in the last month while \input{tables/no_use}\unskip\% do not recall the amount that their household consumed in the previous month.

As a simple way to capture this coordination task, let each household $i$ set a goal for water use each month, $w_i$, knowing that consumption shocks, $\epsilon_i$, may increase or decrease the realized amount of usage.  Consumption shocks, $\epsilon_i$, are assumed to be unobserved to the household and independent across time, bringing the total realized water consumption each month to, $W_i=w_i+\epsilon_i$.  Household utility over water, $W_i$ and a numeraire good, $x_i$ is assumed to take the following shape:
\begin{align}\label{equation:umaxfirst}
\begin{split}
U(x_i,W_i) &=  x_i + (1-H_i) W_i - \frac{1}{2\alpha_i } ( W_i - \Gamma_i + \alpha_i )^2  \\
W_i &= w_i + \epsilon_i \\
\epsilon_i &\sim \mathcal{N}(0,\Sigma_{\epsilon})
\end{split}
\end{align}
Following from quasi-linear preferences, this quadratic form for utility eliminates income effects and includes a natural satiation point for water consumption, capturing the tendency of households to target specific consumption levels despite low or zero marginal prices as in Figure~\ref{figure:consumptionhistogram}.  Household preferences for water are characterized by $\Gamma_i$, which can be interpreted as a fixed preference for water each month and $\alpha_i$, which captures the extent to which households are price sensitive.  These terms have clearer interpretations in the demand function below.  The exogenous shock to consumption, $\epsilon_i$, is assumed to be drawn from a multivariate normal distribution, $\Sigma_{\epsilon}$ with zero mean, variance terms, $\sigma_{\epsilon}^2$, and allowing for correlation with neighboring households, ${\rho}^{\epsilon}_{i,j}$.  Although households cannot anticipate the exact realization of $\epsilon_i$, they are assumed to understand the distribution of possible shocks, allowing them to maximize expected utility.

Households that are using water from a neighbor's tap may face an additional utility cost per gallon of water $H_i$.  This hassle cost captures any inconvenience associated with using water from a neighbor's tap.  The mobile survey reveals that among households accessing water from a neighbor's connection, \input{tables/access_fetch}\unskip\% fetch water with containers, \input{tables/access_single_tap}\unskip\% access water from a single hose/pipe provided by the connection owner, and \input{tables/access_pipes}\unskip\% are able to fully connect their household plumbing near the water meter.  These different modes of access suggest that sharing households may face higher time costs fetching water or lower water pressure from piping water additional distances.  Without data on the sharing mode and distance between households for each connection, the model assumes all sharing households face a homogeneous hassle cost, $H_i$, from using a neighbor's connection.\footnote{Section~\ref{section:hasslecostestimation} discusses the extent to which this assumption may bias estimates.  The partitioning of the city into sharing neighborhoods also imposes the implicit assumption that hassle costs rise substantially between neighborhoods so that no household has an incentive to share with households in another neighborhood.}

% , normalized as $i>1$,

\subsubsection{Determining the Budget Constraint}

The household problem is additionally complicated by the presence of non-linear price schedules for water.  Figure~\ref{figure:tariff} provides the increasing tariff in Manila.  The non-linear price schedule produces kinks in household budget constraints leading to non-linear demand functions.  Let $P(W_C) = \{ p^{1},...,p^{K},\overline{W}^{0},...,\overline{W}^{K}\}$ describe tariff schedule as a function of total consumption for the water connection, $W_C = \sum_{i=1}^{S} W_i$.  The tariff includes $K$ segments where segment $k$ corresponds to price $p^{k}$ for water consumption between the consumption thresholds (or kink points), $\overline{W}^{k-1}$ and $\overline{W}^{k}$:
\begin{align*}
P(W_C)=&  
\begin{cases}
      p^{1} &\text{ if } W_C \in [\overline{W}^{0}(=0),\overline{W}^{1}], \\
      p^{2} &\text{ if } W_C \in [\overline{W}^{1},\overline{W}^{2}], \\
      ...   &\text{ ...}, \\
      p^{K} &\text{ if } W_C \in[\overline{W}^{K-1},\overline{W}^{K}(=\infty)]
    \end{cases}
\end{align*}
Given prices and household utility, the final ingredient for characterizing consumption choices is the budget constraint.  The budget constraint includes monthly household income, $Y_i$, and monthly fixed costs of using the water connection, $F_i$, which are assumed to capture three components: (1) monthly service fees, (2) initial connection fees amortized in monthly terms for the duration of the connection, and (3) unobserved, fixed hassle costs associated with setting up a connection, which are also amortized into monthly terms.  Data does not track household water source choices over time in a comprehensive way, which limits the extent to which the model can distinguish between one-time connection costs and monthly service/maintenance costs.  This limitation means that the model cannot address the optimal timing of fixed payments or capture any potential heterogeneity in monthly fixed costs.

Water sharing relationships impact monthly consumption choices through the budget constraint.\footnote{While the formation of these relationships is discussed in more detail in Section~\ref{section:watersourcechoice}, this section takes these sharing relationships as exogenously given.}  To develop notation for sharing, normalize $i=1$ to be the owner of the connection and define the total number of sharing households for a particular connection as $S$.  Therefore, all households, $i\neq1$, using from a neighbor's tap have a positive hassle cost, $H$, while the connection owner, $i=1$, has zero hassle cost.

This model assumes that the monthly water bill is split evenly between all sharing households.  Descriptive evidence suggests that challenges observing and coordinating usage within members of a household also extend across households.  Among owners of the water connection responding to the mobile survey, \input{tables/bill_split}\unskip\% report splitting the water bill evenly or alternating payment each month, \input{tables/bill_fixed}\unskip\% charge sharing households a fixed amount each month regardless of their consumption, and \input{tables/bill_usage}\unskip\% charge other users a price according to their usage.\footnote{The remaining households report ``I don't know'' or ``other.''}  Evenly splitting the bill, alternating payment, or charging a fixed amount provide easy ways to extract compensation without requiring specific information on the monthly consumption of each sharing household.  Yet, these methods also introduce free-rider incentives since households do not have to fully pay for their contributions to the total water bill.  Since data limitations prevent identifying the specific type of contract associated with each shared connection, the model assumes that all households evenly split the bill and explores the theoretical and empirical implications of alternate models in Appendix~\ref{appendix:fixedprice}.  The model captures bill splitting by dividing the total monthly payment for a water connection across the $S$ sharing households.

%\footnote{Under the additional assumption that households never directly observe the $\epsilon$ shocks, splitting the bill provides an intuitive way to ensure all households account for at least some of their usage.  }

Sharing households must negotiate over how to pay the monthly fixed fees.  The model assumes that households commit to dividing any fixed fees at the start of the sharing arrangement.  Under quasi-linear utility, any fixed transfers are exogenous to monthly consumption decisions.  For ease of exposition, this section assigns a fixed fee, $F_i$ to each household and postpones discussion of how the total fixed fee may be divided between households to Section~\ref{section:watersourcechoice}.

Normalizing the price of the numeraire good, $x$, to one, the budget constraint for household, $i$, using a connection with households, $S$, takes the following form given that total consumption for their connection, $W_C$, falls between thresholds, $\overline{W}^{k-1}$ and $\overline{W}^{k}$:
%\begin{align*}
%Y_i - F_i &=  
%\begin{cases}
%      x_i + H_{i} W_i + \frac{1}{S} p^{1} W_C   &\text{ if }   W_C \in [0,\overline{W}^{1}], \\
%      x_i +  H_{i} W_i +  \frac{1}{S} \big [p^{k} W_C -  E_{k} \big]     &\text{ if } W_C \in [\overline{W}^{k-1},\overline{W}^{k}], \\
%      ...   &\text{ ... }      
%\end{cases} \\
%E_{k} &= \big  [\sum_{j=1}^{k-1}  (p^{k} - p^{j})(\overline{W}^{j}-\overline{W}^{j-1})  \big ]
%\end{align*}
\begin{align}
\label{equation:budgetconstraint}
\begin{split}
(Y_i - F_i) &= x_i +   \dfrac{  B_{C,k}  }{S_C}    \hspace{.3cm} \text{ if } \hspace{.1cm} W_C \in [\overline{W}^{k-1},\overline{W}^{k}] \\
\text{Where: }& \\
B_{C,k}  &= p^{k} (W_{C}^{*} - \overline{W}^{k-1}) +\sum_{j=1}^{k-1}  p^{j}(\overline{W}^{j}-\overline{W}^{j-1}) 
\end{split}
\end{align}

The full budget constraint is a piece-wise expression of equation (\ref{equation:budgetconstraint}) over all $K$ price thresholds.  $B_{C,k}$represents the total water bill for connection $C$ given the tariff schedule.  This term is calculated by subtracting the current price that the household faces, $p^{k}$, from the previous prices and multiplying by their exposure given by, $(\overline{W}^{j}-\overline{W}^{j-1})$.\footnote{In the case where a household uses a connection individually, this expression simplifies by setting the index, $i$, and the total using households, $S$, both equal to one.  In this scenario, the household does not face any hassle costs, $H_i$, and pays the total bill from its corresponding consumption.}

@@

When households share a water connection, the consumption choice for each household becomes a strategic decision.  Since prices are non-linear, the total consumption level for each connection, $W_C$, determines the marginal price faced by all households.  For example, with an increasing block tariff like Figure~\ref{figure:tariff}, one household's choice to increase consumption may produce a higher marginal price for other sharing households.   Rewriting the utility function in equation (\ref{equation:umaxfirst}) by substituting the numeraire good, $x$, with the budget constraint, expected utility for household $i$ over the consumption shocks takes the following form:

%\scalebox{.88}{\parbox{1\linewidth}{
%\begin{align*}
%E[U(x_i,w_i)] = &  (Y_i - F_i)  - \frac{1}{S} \sum_{k=1}^{K} \int_{\overline{W}^{k-1}-W_C}^{\overline{W}^{k}-W_C}\big [p^{k} W_C -  E_{k} \big] d \epsilon_C + \int_{-\infty}^{\infty} W_i - H_{i} W_i - \frac{1}{2\alpha_i} ( W_i - \Gamma_i + \alpha_i )^2 d \epsilon_i  \\  
 %         = &  (Y_i - F_i)  - \frac{1}{S} \sum_{k=1}^{K} \int_{\overline{W}^{k-1}-W_C}^{\overline{W}^{k}-W_C}\big [p^{k} W_C d -  E_{k} \big] d \epsilon_C+ w_i - H_{i} w_i - \frac{1}{2\alpha_i} ( w_i - \Gamma_i + \alpha_i )^2 + \sigma_{\epsilon}^{2}  
%\end{align*}
%}} \\

% E[U(w_i)] = 
\begin{align*}
max_{w_i} \sum_{k=1}^{K} \int_{\overline{W}^{k-1}-{w_C}}^{\overline{W}^{k}-{w_C}} (Y_i - F_i) -  \dfrac{ B_{C,k} }{S_C}     + (1-p_s) W_i   - \frac{1}{2\alpha } ( W_i - \Gamma_i + \alpha_i )^2  d \epsilon_C 
\end{align*}

Where $\epsilon_C$ is the convolution of consumption shocks across sharing households distributed as follows:
\begin{align*}
          \epsilon_C &\sim \mathcal{N}(0,\sigma_{\epsilon_C}^2 = \sum_{i=1}^{S} \sigma_{\epsilon}^2 + \sum_{i=1}^{S} \sum_{j>i}^{S} \sigma_{\epsilon}^2 \rho^{\epsilon}_{i,j} )
\end{align*}
To solve this system, the model assumes that households follow a perfect information, pure-strategy Nash-Equilibrium in choosing consumption.  Using this structure, households compute their best response consumption functions to arrive at a symmetric equilibrium taking consumption for their sharing partners as given.  
% % % % % % % % % % % % % % % % \footnote{  APPENDIX PROVES THIS;  NEED TO GO DEEPER PLEASE!!! SHOW EXPLICITLY }  % % % % % % % % % % % % % % % % % % %
%Because of the quadratic shape of the utility function, the exogenous shock to consumption, $\epsilon_s$, only affects the optimal consumption choice to the extent that it pushes the household across price thresholds.  Therefore, the solution to equation (\ref{equation:umaxfirst}) is isomorphic to removing the $\epsilon_s$ terms from the utility function and only allowing these shocks to enter through the budget constraint.  This simplification ensures that the $\epsilon_s$ terms enter linearly into the optimization problem through the budget constraint.

@@

The best-response functions for each household can be solved and summed across all sharing households $S$ to form demand at the level of each connection, $C$.  The optimal demand function takes a piecewise form depending on the proximity of different price segments.\footnote{This approach is only relevant for strictly increasing block tariffs since in this case, the budget constraint is convex.  Tariffs that include both increasing and decreasing block tariffs require comparing indirect utilities across all segments.  I take this calculation into account when allowing for decreasing marginal prices in the counterfactual exercises.}  The aggregate demand function is as follows (where $L,M,H$ index low, medium, and high prices relative to each segment):
\begin{align}\label{equation:generaldemand}
\begin{split}
w^{*}_C &=
\begin{cases}
D^{1}_C   & \text{ if } \hspace{1.7cm}                                               \frac{ \eta_C }{ V_{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
D^{1,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
D^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
D^{2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
D^{3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
D^{3,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
D^{4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
\end{cases}\\
\text{Where: } & \\
D^{L,M,H}_C        		&=  d^{L,M,H}_C + \frac{ \eta_C }{ V_{L,H} }   \\
d^{L,M,H}_C       		&= \frac{ 1}{ V^{L,H} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{H} + p^{L} - \overline{W}^{H} (\frac{p^{H} - p^{M}}{\sqrt{2}{\sigma_{\epsilon_C}}})  - \overline{W}^{M} (\frac{p^{M} - p^{L}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ]  \Big )    \\
V^{L,H} 	     	    &=   1 + \frac{\alpha_C}{2 S} ( \frac{p^{H} - p^{L}}{\sqrt{2}\sigma_{\epsilon_C}})   \\
\overline{\eta}^{j}_{l,L}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) - \sqrt{2} \sigma_{\epsilon_C} \\
\overline{\eta}^{j}_{l,U}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) + \sqrt{2} \sigma_{\epsilon_C} \\
\end{split}
\end{align}

%\begin{align}\label{equation:generaldemand}
%\begin{split}
%w^{*}_C &=
%\begin{cases}
%D^{1}_C   & \text{ if } \hspace{1.7cm}                                               \frac{ \eta_C }{ V_{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
%D^{1,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
%D^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
%D^{2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
%D^{3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
%D^{3,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
%D^{4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
%\end{cases}\\
%\text{Where: } & \\
%D^{L,M,H}_C        		&=  d^{L,M,H}_C + \frac{ \eta_C }{ V_{H,L} }   \\
%d^{L,M,H}_C       		&= \frac{ 1}{ V^{L,H} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{H} (\tfrac{\lambda_C - \overline{W}^{H}}{\lambda_C}) + p^{M} (\tfrac{\overline{W}^{H} - \overline{W}^{H}}{\lambda_C} ) -    p^{L} - \overline{W}^{H} (\frac{p^{H} - p^{M}}{\lambda_C})  - \overline{W}^{M} (\frac{p^{M} - p^{L}}{\lambda_C})  ]  \Big )    \\
%V^{L,H} 	     	    &=   1 + \frac{\alpha_C}{2 S} ( \frac{p^{H} - p^{L}}{\lambda_C})  ,  \lambda_C = \sqrt{2}{\sigma_{\epsilon_C}} \\
%\overline{\eta}^{j}_{l,L}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) - \lambda_C \\
%\overline{\eta}^{j}_{l,U}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) + \lambda_C \\
%\end{split}
%\end{align}

For ease of exposition, I use notation where $D^{l}_C=D^{l,l,l}_C$ and $D^{l,j}_C=D^{l,j,j}_C$.
